---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# wbmacro

<!-- badges: start -->
[![R-CMD-check](https://github.com/hwiminPark/DATA534-Group-7/actions/workflows/R-CMD-check.yml/badge.svg?branch=github-actions)](https://github.com/hwiminPark/DATA534-Group-7/actions/workflows/R-CMD-check.yml)
<!-- badges: end -->

**wbmacro** is an R package that provides a clean, tidyverse-friendly interface to the **World Bank Indicators API**.

It lets users:
- Search for macroeconomic/development indicators
- List and filter countries/regions
- Fetch time-series data for one or more indicators/countries/years
- Quickly visualize trends with ggplot2

The package returns analysis-ready tibbles and focuses on cross-country comparisons over time (e.g. GDP per capita, population growth, inflation).

## Installation

You can install the development version from GitHub:

``` r
# install.packages("devtools")
devtools::install_github("yourusername/wbmacro")
```

## Quick start

```{r example, message=FALSE}
library(wbmacro)
library(dplyr)
library(ggplot2)

# 1. Discover indicators
wb_search_indicators("gdp per capita") |>
  select(indicator_id, name, unit) |>
  slice_head(n = 5)

# 2. Fetch data for a few countries (2015–2023)
dat <- wb_fetch(
  indicators = c("NY.GDP.PCAP.KD", "SP.POP.GROW"),
  countries  = c("CAN", "USA", "CHN", "DEU", "IND"),
  start_year = 2015,
  end_year   = 2023
)

# 3. Plot trends
wb_plot_trends(
  dat |> filter(indicator_id == "NY.GDP.PCAP.KD"),
  color_by = "country",
  title = "GDP per capita (constant 2015 US$) – Selected Countries"
)
```

For a full end-to-end example (search → filter countries → fetch → plot), see the vignette:

``` r
vignette("comparing-macro-trends", package = "wbmacro")
```

## Features

- Tidy output (long format tibbles ready for `dplyr`/`ggplot2`)
- Pagination handling for large requests
- Basic input validation & friendly error/fallback messages
- Quick plotting helper (`wb_plot_trends()`)
- Focus on comparative macroeconomic analysis

## Development status

- Core functions implemented and tested
- Vignette complete
- Tests passing locally & in CI
- Aiming for clean `R CMD check` results

## Contributing

Please read [CONTRIBUTING.md](CONTRIBUTING.md) for details on our code of conduct and pull request process.
